Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-08-09 manuscript/main.tex
begin R1 response

This analysis allowed us to establish links between microbial taxa and
their functional potential with cognition and brain structure. Although
we cannot test causality or the chemistry behind the interactions
between gut microbial taxa and their genes, the gut, and the brain,
this study provides clear and statistically significant associations
between the infant and early child gut microbiota and neurocognition.
Future studies should focus on characterizing the early-life microbiome
and neurocognitive development across different geographic regions
and lifestyles such as covering traditionally understudied populations,
such as low-resource urban, peri-urban and rural communities
to obtain the more comprehensive understanding of the
variability within the different gut microbiomes reflects on
neurocognition. These studies would also provide us with the wealth of
data on different strains from the same species to better understand the
effect of genes and their products. Furthermore, culturing and microbial
community enrichment studies combined with genetic manipulation and
genomic approaches to understand microbial metabolism at the molecular
level is key, as the metabolic functions shape and influence the
human host and its health. The discovery of the neuroactive metabolites
could provide us with biomarkers for early detection or necessary
medicinally useful molecules that can be applied in intervention.

@@

This research was funded by NIH UG3 OD023313 and Wellcome LEAP 1kD.
The authors declare that they have no competing interests.

>>>>

This analysis allowed us to establish links between microbial taxa and
their functional potential with cognition and brain structure. 
Although we did not directly test the causal relationships
between gut microbial taxa and their genes, the gut, and the brain,
this study provides clear and statistically significant associations
that could serve as targets for future efforts in pre-clinical models.
For example, mouse models of brain development, learning, and executive function
could be assessed in germ-free animals with the addition of
metabolically characterized and manipulated microbes.
Future studies should also focus on characterizing the early-life microbiome
and neurocognitive development across different geographic regions
and lifestyles such as covering traditionally understudied populations,
such as low-resource urban, peri-urban and rural communities
to obtain the more comprehensive understanding of the
variability within the different gut microbiomes reflects on
neurocognition. These studies would also provide us with the wealth of
data on different strains from the same species to better understand the
effect of genes and their products. Furthermore, culturing and microbial
community enrichment studies combined with genetic manipulation and
genomic approaches to understand microbial metabolism at the molecular
level is key, as the metabolic functions shape and influence the
human host and its health. The discovery of the neuroactive metabolites
could provide us with biomarkers for early detection or necessary
medicinally useful molecules that can be applied in intervention.

@@

This research was funded by NIH UG3 OD023313 and Wellcome LEAP 1kD.
The authors declare that they have no competing interests.
We thank Libusha Kelly (Albert Einstein School of Medicine) and Daphne Koinis Mitchell (Brown University)
for helpful feedback on the manuscript. The research team also thanks the participants and families
of the participants who generously shared their time and samples for this project.
